---
title: "Processing chinstrap penguin Axy trek data"
author: "Lucas Krüger"
date: "`r Sys.Date()`"
output: html_document
---

# first lets load packages

```{r}


library(track2KBA)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sp)
library(adehabitatHR)
library(bsam)
library(ggplot2)
library(patchwork)


```


### then load and prepare data

```{r}

setwd("D:/UruguayPenguins/Harmony")


GPS_HP<-readRDS("HP_GPS_2019_2021_2022.Rds") # raw GPS data
Dives_HP<-readRDS("HP_Dives_2019_2021_2022.Rds") # dive data processed previously using DiveMove


GPS_HP$date<-as.POSIXct(strptime(GPS_HP$Timestamp, format="%d/%m/%Y %H:%M:%S", tz="GMT"))

dfSM<-plyr::ddply(GPS_HP, c("TagID","date"), summarise,
                  lon=mean(location.lon),lat=mean(location.lat))

dfSM <- dfSM[!duplicated(dfSM[, c("lat", "lon","date")]), ]


#check if there are potentially wrong GPS fixes

dfSM<-subset(dfSM,lat>(-63))
ggplot(dfSM,aes(lon,lat))+geom_point()



dfMP<-data.frame(id=dfSM$TagID,date=dfSM$date,lc=c(3),lon=dfSM$lon,lat=dfSM$lat) # using the maximum accuracy in argos data

dfMP$id<-paste(dfMP$id,year(dfMP$date))

summary(as.factor(dfMP$id))


dfMG<-data.frame(id=dfSM$TagID,date=dfSM$date,lc=c("G"),lon=dfSM$lon,lat=dfSM$lat,
                 lonerr=c(0.0001),laterr=c(0.0001)) # specifying lat and long errors 0.0001 degrees, around 11m

dfMG$id<-paste(dfMG$id,year(dfMG$date))


```


###testing parameters with a single individual
### i did several tests with different tstep, thin and span, but only kept the values
### that produced good predictions

```{r}


ggplot(data=subset(dfMP,id=="HP-11_S1 2020"),aes(lon,lat))+geom_point()
summary(dfMP$date[dfMP$id=="HP-11_S1"])

bs0<-fit_ssm(data=subset(dfMP,id=="HP-11_S1 2020"),model="DCRW",tstep = 0.006, adapt = 50, samples = 2000, 
             thin = 5, span = 0.05) # large samples with small span resulted in better predictions
                                   #processing took 4.4 minutes for one animal

diag_ssm(bs0) # statistical diagnostics are very good

map_ssm(bs0)+theme_bw() # spatial predictions are good


bs0b<-fit_ssm(data=subset(dfMG,id=="HP-11_S1 2020"),model="DCRW",tstep = 0.006, adapt = 50, samples = 2000, 
             thin = 5, span = 0.05) # large samples with small span resulted in better predictions
                                    #processing took 5.1 minutes for one animal

diag_ssm(bs0b) # statistical diagnostics are really good

map_ssm(bs0b)+theme_bw() # spatial predictions are  good, but the previous was better


#comparison


map_ssm(bs0)+theme_bw()+ggtitle(label="a. ARGOS location quality class 3")+
map_ssm(bs0b)+theme_bw()+ggtitle(label="b. Fixed geographical error of 0.0001") 
# using argos quality class 3 yielded better predictions



```

### once we found the better method and optimal parameterization, lets apply to all data

```{r}

head(dfMP)
#ggplot(dfMP,aes(date,lat))+geom_point()

dfMP19<-subset(dfMP,date<'2021-01-01')
dfMP21<-subset(dfMP,date>'2021-01-01' & date<'2022-11-01')
dfMP22<-subset(dfMP,date>'2022-12-31')

bs19<-fit_ssm(dfMP19,model="DCRW",tstep = 0.0065, adapt = 50, samples = 2000, 
             thin = 5, span = 0.05)

diag_ssm(bs19)

map_ssm(bs19)+theme_bw()


bs21<-fit_ssm(dfMP21,model="DCRW",tstep = 0.0065, adapt = 50, samples = 2000, 
              thin = 5, span = 0.05)

diag_ssm(bs21)

map_ssm(bs21)+theme_bw()

bs22<-fit_ssm(dfMP22,model="DCRW",tstep = 0.0065, adapt = 50, samples = 2000, 
              thin = 5, span = 0.05)

diag_ssm(bs22)

map_ssm(bs22)+theme_bw()


map_ssm(bs19)+theme_bw()+ggtitle(label="a. Observed and modeled geographical positions for 2019/20")+
  map_ssm(bs21)+theme_bw()+ggtitle(label="b. Observed and modeled geographical positions for 2021/22")+
  map_ssm(bs22)+theme_bw()+ggtitle(label="c. Observed and modeled geographical positions for 2022/23")

ssm19<-get_summary(bs19)
ssm21<-get_summary(bs21)
ssm22<-get_summary(bs22)


ssm.df<-rbind(ssm19,ssm21,ssm22)
```


### now lets interpolate positions based on dives beggining of descent 

```{r}
head(DivesHP)

peng_track <- as.ltraj (xy = ssmdf[,c("lon","lat")], date = ssmdf$date,
                        id = ssmdf$Id,
                        burst = ssmdf$Id,
                        proj4string = crs) 


mtrack <- move(peng_track) 

spo=CRS('+init=epsg:3031')

move_track<-spTransform(mtrack,CRSobj=spo,center=FALSE)

plot(move_track)

summary(gpsdf$date)
summary(DivesHP$begdesc)

TDRm<-subset(DivesHP,begdesc<max(gpsdf$date))
TDRm<-subset(TDRm,begdesc>min(gpsdf$date))

# Aggregate interpolated location
track_interpolated <- data.frame() 

# for(i in 1:length(move_track@idData$burst)) { # each trip
i = 1
track_sel <- move_track[[i]]

# name <- track_sel@idData$burst # keep the names
t_interp <- interpolateTime(move_track, time=Dives_HP$begdesc, spaceMethod='euclidean') # Interpolating for the beggining of dive descent
plot(move_track, col="red",pch=20, main="By custom timestamps")
points(t_interp)
lines(move_track[[i]], col="red")
legend("bottomleft", c("True locations", "Interpolated locations"), col=c("red", "black"), pch=c(20,1))
t_interp_df <- as.data.frame (t_interp) # Interpolated positions
t_record_df <- as.data.frame (move_track) # SSM positions

t_interp_df <- rbind (t_interp_df, t_record_df) %>%  # both together
  arrange (timestamps)

TDRm$timestamps<-TDRm$begdesc

tdrgpsdf<-merge(t_interp_df,TDRm,by="timestamps")

saveRDS(tdrgpsdf,"DiveLocations.Rds")
